Well-quasi-orderings on word languages \\ main 81b14ea82bdf369ba5dbe8de29fa418756900125 \\ 2025-10-15 17:43:32 +0200

### 2025-10-16 wqo-on-words.lncs.tex
fix: moving stuff to appendix
Add thmtools integration and demonstrate restatable theorem proof of concept
Co-authored-by: AliaumeL <24816735+AliaumeL@users.noreply.github.com>

%! TEX program = pdflatex
% WARNING: this is a generated file.
%
% Please do not edit this file directly. 
% - If you want to update the medatata of the paper (title, authors, abstract), please
%   edit the `paper-meta.yaml` file in the root of the repository.
% - If you want to update the content of the paper, please edit the latex files
%   in the `src` directory.
% - If you want to update the template itself (e.g., change the layout), please
%   edit the `templates/lncs/lncs.tex` file instead.
\documentclass[runningheads]{llncs}

@@

% microtype for better typography
\usepackage{microtype}

@@

>>>>

%! TEX program = pdflatex
% WARNING: this is a generated file.
%
% Please do not edit this file directly. 
% - If you want to update the medatata of the paper (title, authors, abstract), please
%   edit the `paper-meta.yaml` file in the root of the repository.
% - If you want to update the content of the paper, please edit the latex files
%   in the `src` directory.
% - If you want to update the template itself (e.g., change the layout), please
%   edit the `templates/lncs/lncs.tex` file instead.
\documentclass[runningheads,envcountsame]{llncs}

@@

% microtype for better typography
%\usepackage{microtype} % Disabled due to font expansion issues

@@

% Redefine theorem environments to be compatible with thmtools restatable
% llncs.cls already defines these using \spnewtheorem, but we need them to work with thmtools
% We need to undefine both the environments and the counters
\makeatletter
\let\theorem\relax
\let\endtheorem\relax
\let\c@theorem\relax
\let\thetheorem\relax
\let\p@theorem\relax
\let\lemma\relax
\let\endlemma\relax
\let\c@lemma\relax
\let\thelemma\relax
\let\p@lemma\relax
\let\corollary\relax
\let\endcorollary\relax
\let\c@corollary\relax
\let\thecorollary\relax
\let\p@corollary\relax
\let\proposition\relax
\let\endproposition\relax
\let\c@proposition\relax
\let\theproposition\relax
\let\p@proposition\relax
\let\definition\relax
\let\enddefinition\relax
\let\c@definition\relax
\let\thedefinition\relax
\let\p@definition\relax
\let\example\relax
\let\endexample\relax
\let\c@example\relax
\let\theexample\relax
\let\p@example\relax
\let\remark\relax
\let\endremark\relax
\let\c@remark\relax
\let\theremark\relax
\let\p@remark\relax
\makeatother

% Now redeclare them using thmtools for restatable support
% Using llncs-like formatting: bold for theorem names, italic for body
\declaretheorem[style=plain,numberwithin=section,name=Theorem]{theorem}
\declaretheorem[style=plain,sibling=theorem,name=Lemma]{lemma}
\declaretheorem[style=plain,sibling=theorem,name=Corollary]{corollary}
\declaretheorem[style=plain,sibling=theorem,name=Proposition]{proposition}
\declaretheorem[style=definition,sibling=theorem,name=Definition]{definition}
\declaretheorem[style=definition,sibling=theorem,name=Example]{example}
\declaretheorem[style=remark,sibling=theorem,name=Remark]{remark}
